\pagebreak
\section{Infinite Sets}

\bx{ % 0.6.1
    \ea{
        \item Show that the set of rational numbers is countable (i.e., that you can list all rational numbers).
        \item Show that the set of $\mathbb D$ of finite decimals is countable.
    }
    \sol{
        \ea{
            \item Let
            \[
                A=\{(p,q)\in\mathbb Z\times\mathbb N:q>0,\ \gcd(p,q)=1\}.
            \]
            Every rational number has a unique representation
            \[
                r=\frac pq,\qquad (p,q)\in A.
            \]
            Since $\mathbb Z$ and $\mathbb N$ are countable, the Cartesian product
            $\mathbb Z\times\mathbb N$ is countable. Hence $A$, being a subset of
            $\mathbb Z\times\mathbb N$, is also countable.

            Define
            \[
                f:A\to\mathbb Q,\qquad
                f(p,q)=\frac pq.
            \]
            By uniqueness of the reduced form, $f$ is one-to-one, and by definition
            every rational number is of the form $p/q$ with $(p,q)\in A$, so $f$ is
            onto. Thus $f$ is a bijection, and therefore $\mathbb Q$ is countable.

            \item Every finite decimal can be written in the form
            \[
                \frac{k}{10^n},
            \]
            where $k\in\mathbb Z$ and $n\in\mathbb N\cup\{0\}$. Define
            \[
                g:\mathbb D\to\mathbb Z\times(\mathbb N\cup\{0\}),\qquad
                g\!\left(\frac{k}{10^n}\right)=(k,n),
            \]
            where the decimal is written without trailing zeros.

            This map is one-to-one. Since $\mathbb Z\times(\mathbb N\cup\{0\})$ is
            countable, its subset $\mathbb D$ is also countable.
        }
    }
}

\bx{ % 0.6.2
    \ea{
        \item Show that if $E$ is finite and has $n$ elements, then the power set $\mathcal P(E)$ has $2^n$ elements.
        \item Choose a map $f  :  \{a, b, c\} \rightarrow \mathcal P(\{a, b, c\})$, and compute for that map the set $\{ x | x \notin f(x) \}$. Verify that this set is not in the image of $f$.
    }
    \sol{\ea{
        \item Number the elements of $E$ as $e_1,\dots,e_n$. To form a subset $X \subseteq E$, for each element $e_i$ we have exactly two choices:
            \[
            e_i \in X \qquad \text{or} \qquad e_i \notin X.
            \]
            These choices are independent, so by the multiplication principle there are
            \[
            \underbrace{2 \times 2 \times \cdots \times 2}_{n\text{ times}} = 2^n
            \]
            possible choices. Moreover, each sequence of choices determines a unique subset of $E$, and every subset arises in this way. Hence $\mathcal P(E)$ has exactly $2^n$ elements.

        \item Define $f(x) = \{x\}$. Then $\{x | x \notin f(x)\} = \emptyset$, which is not in the image of $f$.
        }   
    }
}

\pagebreak
\bx{ % 0.6.3
    Show that $(-1 , 1)$ has the same infinity of points as the reals.\ \textit{Hint}: Consider the function $g(x) = \tan (\pi x /2)$.
    \sol{
        Considering the function $g(x) = \tan (\pi x /2)$ over the domain $(-1,1)$, we get the mapping $ g : (-1,1) \rightarrow \R$. We will now show that $g$ is a bijection.

        Calculating the derivative of $g$, gives us $g'(x) = \frac\pi2 \sec^2 ( \pi x /2) > 0$ for all $x \in (-1, 1)$. Since $g$ is continuous and strictly increasing on $(-1,1)$, $g$ is one to one.

        To show that $g$ is onto, let 
        \[
        \tan \left(\frac{\pi x}2 \right) = y \implies \frac{\pi x}2 = \tan^{-1} (y) \in \left( -\frac\pi2, \frac\pi2 \right)
        \] 
        Then 
        \[
        -\frac\pi2 < \frac{\pi x}2 < \frac\pi2 \implies -1 < x < 1 \implies x \in (-1, 1)
        \]
        Thus showing that for every $y \in \R$, there exists $x \in (-1,1)$ such that $g(x) = y$, implying that $g$ is onto and therefore a bijection.

        We have thus shown that $(-1 , 1) \asymp \R$.
    }
}

\bx{ % 0.6.4
    \ea{
        \item How many polynomials of degree $d$ are there with coefficients with absolute value $ \le d $?
        \item Give an upper bound for the position in the list of formula 0.6.5 of the polynomial $x^4 - x^3 + 5$.
        \item Give an upper bound for the position of the real cube root of $2$ is the list of numbers made from the list of formula 0.6.5.
    }
    \sol{
        \ea{
            \item Let $p_d(x) = a_d x^d + a_{d-1} x^{d-1} + \cdots + a_0$ be a polynomial of degree $d$, with $|a_i| \le d$ and $a_d \ne 0$.
            
            To find the number of polynomials, we will consider the number of cases for each coefficient. 

            For $a_d$,
            \[
            a_d \in \{-d, -d+1, \dots, d-1, d\} \setminus \{0\}
            \]
            which can take $(2d)$ possible values.

            For $a_i$, $i < d$, 
            \[
            a_i \in \{-d, -d+1, \dots, d-1, d\}
            \]
            which can take $(2d+1)$ possible values.

            Since each coefficient is independent, by the multiplication principle, there are 
            \[
            (2d) \times \underbrace{(2d+1) \times \cdots \times (2d+1)}_{(d) \text{ times}} = (2d)(2d+1)^{d}
            \]
            possible polynomials of degree $d$.

            \item Let $P_d$ be the number of polynomials of degree $d$ or lower, with coefficients with absolute value $ \le d$ and $p_i$ be the polynomial with index position $i$. Then using similar reasoning to above, $P_d = (2d+1)^{d+1}$.
            
            While $x^4 - x^3 + 5$ is a polynomial of degree $4$, the coefficient of $x^0$ is $5$, hence it must be within the first $P_5$ polynomials, thus the upper bound for the position of the polynomial $x^4 - x^3 + 5$ is $P_5 = 11^6$.

            \item Similarly, $x^3 - 2$ will be within the first $P_3$ polynomials. Since each polynomial would have at most $3$ roots, we will have an upper bound of 
            \[
            3 P_3 = 3 \times 7^4
            \] for the position in the list of numbers made from the list of formula 0.6.5.
        }
    }
}

\bx{ % 0.6.5
    Let $f : A \rightarrow B$ and $g : B \rightarrow A$ be one to one. We will sketch how to construct a mapping $h : A \rightarrow B$ that is one to one and onto.

    Let an $(f, g)$-chain be a sequence consisting alternately of elements of $A$ and $B$, with elements following an element $a \in A$ being $f(a) \in B$, and the element following an element $b \in B$ being $g(b) \in A$. 
    \ea{
        \item Show that every $(f,g)$-chain can be uniquely continued forever to the right, and to the left can \en{
            \item either be uniquely continued forever, or
            \item can be continued to an element of $A$ that is not in the image of $g$, or 
            \item can be continued to an element of $B$ that is not in the image of $f$.
        }
        \item Show that every element of $A$ and every element of $B$ is an element of a unique such maximal $(f,g)$-chain.
        \item Construct $h : A \rightarrow B$ by setting 
            \[
            h(a) = \begin{cases*}
            f(a)      & if $a$ belongs to a maximal chain of type 1 or 2 above, \\
            g^{-1}(a) & if $a$ belongs to a maximal chain of type 3.
            \end{cases*}
            \]
            Show that $h : A \rightarrow B$ is well defined, one to one, and onto.
        
        \item Take $A = [-1, 1]$ and $B = (-1, 1)$. It is surprisingly difficult to write a mapping $h : A \rightarrow B$. Take $f : A \rightarrow B$ defined by $f(x) = x/2$, and $g : B \rightarrow A$ defined by $g(x) = x$.
        
        What elements of $[-1, 1]$ belong to chains of type 1, 2, 3?

        What map $h : [-1,1] \rightarrow (-1,1)$ does the construction in part c give?
    }
    \sol{
        \ea{
            \item We first show that every $(f,g)$-chain can be uniquely continued forever to the right.

            Suppose $a \in A$. Since $f : A \rightarrow B$ is a function,
            $
            f(a) \in B
            $
            exists uniquely. Likewise, since $g : B \rightarrow A$ is a function,
            $
            g(f(a)) \in A
            $
            exists uniquely. Repeating this argument inductively gives the infinite chain
            $
            a,\; f(a),\; g(f(a)),\; f(g(f(a))),\; \dots
            $
            Thus every $(f,g)$-chain can be uniquely continued forever to the right.

            We now consider continuation to the left. Let
            \[
            A^* = A \setminus g(B), \qquad
            B^* = B \setminus f(A).
            \]

            Suppose first that the current element of the chain is $a \in A$. To continue one step to the left we require an element $b \in B$ satisfying
            $
            g(b)=a.
            $
            If $a \in g(B)$, then such a $b$ exists. Since $g$ is one to one, this $b$ is unique. If instead $a \in A^*$, then no such $b$ exists, and the chain terminates on the left at $a$. This gives case (2).

            Similarly, suppose the current element is $b \in B$. To continue one step to the left we require an element $a \in A$ satisfying
            $
            f(a)=b.
            $
            If $b \in f(A)$, then such an $a$ exists and is unique since $f$ is one to one. If instead $b \in B^*$, then no such $a$ exists, and the chain terminates on the left at $b$. This gives case (3).

            Finally, if neither of the above situations ever occurs, then every element encountered has a unique predecessor. Hence the chain can be uniquely continued indefinitely to the left, giving case (1). Since exactly one of these three possibilities must occur, every $(f,g)$-chain satisfies exactly one of the stated cases.
            \pagebreak
            \item Let $x \in A \cup B$. We construct the maximal $(f,g)$-chain containing $x$.

            Starting from $x$, repeatedly apply $f$ and $g$ to extend the chain to the right. By part (a), this can be done uniquely forever. 
            Similarly, repeatedly extend the chain to the left whenever a predecessor exists. Again by part (a), each predecessor, when it exists, is unique. 
            This process either continues forever or terminates at an element of $A^*$ or $B^*$. 
            Hence every element of $A \cup B$ belongs to a maximal $(f,g)$-chain.

            It remains to show uniqueness. 
            Suppose $x$ belongs to two maximal chains $C_1$ and $C_2$. Since the predecessor and successor of every element are uniquely determined whenever they exist, 
            both chains must have exactly the same elements to the left and to the right of $x$. Thus $C_1=C_2$.
            Therefore every element of $A$ and every element of $B$ belongs to a unique maximal $(f,g)$-chain.

            \item Firstly, we will show that the function is well defined.
            If $a$ belongs to a maximal chain of type 1 or 2, each element of $a$ would have a subsequent term since every sequence can be uniquely continued forever to the right. Thus, the term $f(a)$ exists, thus there exists an image for $a$.

            If $a$ belongs to a maximal chain of type 3, then the first term of the chain belongs to the set $B$. Since every $a$ has a preceding term, which is equivalent to $g^{-1}(a)$. Thus the inverse exists. 

            Since every term has an image, $h$ is well defined.

            $h$ is one to one. Suppose we have $a_1, a_2 \in A$, such that $h(a_1) = h(a_2)$ but $a_1 \ne a_2$. If both $a_1$ and $a_2$ belong to the a maximal chain of type 1 or 2, then $h(a_1) = f(a_1)$ and $h(a_2) = f(a_2)$, implying $f(a_1) = f(a_2)$, which a contradiction since $f$ is one to one. Similarly, if both $a_1$ and $a_2$ belong to the a maximal chain of type 3, then $h(a_1) = g^{-1} (a_1)$ and $h(a_2) = g^{-1} (a_2)$, implying that $g^{-1} (a_1) = g^{-1} (a_2)$. This is a contradiction as $g$ is one to one, hence $g^{-1}$ is one to one.

            Lastly, we have to consider the case where $h(a_1) = f(a_1)$ and $h(a_2) = g^{-1}(a_2)$. Let $h(a_1) = h(a_2)$, then $f(a_1) = g^{-1}(a_2)$. Since $g$ is one to one, applying $g$ on both sides gives us $g \circ f (a_1) = a_2$. However, this means that both $a_1$ and $g \circ f (a_1) = a_2$ belong to the same chain, which leads to a contradiction.

            Lastly, we will show that $h$ is onto. We need to show that for every $b \in B$, there exists $a \in A$ such that $b = h(a)$. We use the fact that if $a$ is in the chain, then $f(a)$ and $g^{-1}(a)$ (if it exists) are both in the chain. Hence we can construct the inverse
            \[
            h^{-1} (b) = 
            \begin{cases*}
            f^{-1} (b) & if $b$ belongs to a maximal chain of type 1 or 2, \\
            g(b) & if $b$ belongs to a maximal chain of type 3
            \end{cases*}
            \]
            If $b \in B$ is from chains of type 1 and 2, then $b \in f(A)$ so $b = f(a) = h(a)$. Similarly, if $b$ is from chains of type 3, then $h(g(b)) = g^{-1} (g(b)) = b$. Thus having a preimage and hence onto

            \item Note that $f(A) = f( [-1, 1] ) = [-1/2, 1/2]$ and $g(B) = g( (-1, 1) ) = (-1, 1)$, giving us 
            \[
            A^* = A \setminus g(B) = \{ -1,  1\}
            \quad
            \text{and}
            \quad
            B^* = B \setminus f(A) = (-1, -1/2) \cup (1/2, 1)
            \]
            For elements in $A^*$, there does not exist $g^{-1}(A^*)$, hence belonging to chains of type 2. 
            With the first terms being $\pm 1$, all terms in the chain are in the form of $\pm 2^{-n}$ for $n \in \N$; proving this is trivial and hence left as an exercise for the reader.

            The starting elements of the chains of type 3 are $B^*$, and hence the elements from $A$ that are in this chain are $g(B^*) = B^*$. Since $g \circ f (x)  = \frac x2$, the subsequent terms in the chain come from the set 
            \[
            \bigcup_{n=0}^\infty [(-2^{-n}, -2^{-n-1}) \cup (2^{-n-1}, 2^{-n})] = [-1,1] \setminus \bigcup_{n=0}^\infty \{ \pm 2^{-n} \}
            \]

            Let $S_n$ be the set of numbers from $A$ that belong to a maximal chain of type $n$. Since $S_2 \cup S_3 = A$, we can conclude that there are no elements that belong to chains of type 1.

            Using part c, we can construct $h : A \rightarrow B$ that is one to one and onto 
            \[
            h(x) = 
            \begin{cases}
            x/2 & x \in \{ \pm 2^{-n} : n \in \N_0\} \\
            x & \text{else} 
            \end{cases}
            \]

        }
    }
}

\bx{ % 0.6.6
    Show that the points of the circle 
    $
    \displaystyle \left\{ 
    \begin{pmatrix}
        x \\ y
    \end{pmatrix}
    \in \mathbb R^2 \ | \ x^2 + y^2 = 1 \right\}
    $ 
    have the same infinity of elements as $\mathbb R$.\ \textit{Hint}: This is easy if you use Bernstein's theorem (Exercise 0.6.5)

    \sol{
        We will use Bernstein's Theorem from Exercise 0.6.5, by firstly finding to injective maps.

        Let us define
        \[
        S = \left\{ \begin{pmatrix}
        x \\ y
        \end{pmatrix} \in \R^2 \ | \ x^2 + y^2 = 1 \right\}
        \]

        We will construct the map $f : S \rightarrow \R$ as follows 
        \[
            f(x,y) = 
            \begin{cases}
            x + 1 & y \ge 0 \\ 
            x - 1 & y < 0
            \end{cases}
        \]
        $f$ is one to one. Suppose we have $(x_1,y_1), (x_2, y_2) \in S$ such that $(x_1, y_1) \ne (x_2, y_2)$ but $f(x_1, y_1) = f(x_2, y_2)$. 
        If both $y_1, y_2 \ge 0$ or $y_1, y_2 < 0$, $x_1 \ne x_2$; otherwise both points are the same point given that $y = \sqrt{1 - x^2}$ is one to one.
        If $y_1 \ge 0$ and $y_2 < 0$, then $f(x_1, y_1) = f(x_2, y_2)$ implies $x_1 + 1 = x_2 - 1 $ which is not possible. The two x coordinates must differ by 2, which is only possible if $x_1 = -1$ and $x_2 = 1$. However, this results in $y_1 = y_2 = 0$, leading to a contradiction on $y_2 < 0$.

        Now, we construct the map $g : \R \rightarrow S$ as follows 
        \[
            g(x) = \left( \cos (\tan^{-1} x), \sin(\tan^{-1} x) \right) = \left( \frac1{\sqrt{1+x^2}} , \frac x{\sqrt{1+x^2}} \right)
        \]
        $g$ is clearly injective as $\tan^{-1}$ is injective and, $\sin$ and $\cos$ is also injective. By the composition of injective functions, $g$ is also injective.

        Since we have $f : S \rightarrow \R$ and $g: \R \rightarrow S$ that are both one to one, we can use Bernstein's Theorem to construct $h: S \rightarrow \R$ that is both one to one and onto, showing that $S \asymp \R$.
    }
}

\bx{ % 0.6.7
    \ea{
        \item Show that $[0,1) \times [0,1)$ has the same cardinality as $[0,1)$.
        \item Show that $\R^2$ has the same infinity as $\R$.
        \item Show that $\R^n$ has the same infinity as $\R$.
    }
    \sol{
        \item Consider the following notation 
        \[
        a = 0.\overline{a_1 a_2 a_3 \dots} = \sum_{n=1}^\infty \frac{a_n}{10^n}
        \]

        To remove ambiguity, all $a \in [0,1)$ will be expressed in the decimal expansion with recurring 9s. For example, $a = \frac 12$ will be expressed as $0.4999\dots$ and not $0.5000\dots$.

        Define 
        \[
        S = \{ (x,y) : x,y\in [0,1)\}
        \]

        We will now begin the proof. We will define $f_0 : S \rightarrow [0,1)$ as follows:
        \[
        f_0(0.\overline{a_1 a_2 a_3 \dots}, 0.\overline{b_1 b_2 b_3 \dots}) 
        =
        0.\overline{a_1 b_1 a_2 b_2 a_3 b_3 \dots}
        \]
        \textbf{Injective:} Let $(a,b), (c,d) \in S$, such that $(a,b) \ne (c,d)$. We will show that $f_0(a, b) \ne f_0(c,d)$. 
        \[
        f_0(a, b) = 0.\overline{a_1 b_1 a_2 b_2 \dots}, \quad f_0(c,d) = 0.\overline{c_1 d_1 c_2 d_2 \dots}
        \]
        Since $(a,b) \ne (c,d)$ we can find either $a_n \ne c_n$ or $b_n \ne d_n$, showing that the images are not the same. All values are in decimal expansions with recurring 9s, ensuring that there are not two elements in the domain that will map to the same image. 

        Define $f_1 : [0,1) \rightarrow S$ as follows: $f_1(x) = (x, x)$, which is trivially injective. Thus we can construct $f : S \rightarrow [0,1)$ that is bijective by Bernstein’s Theorem.
%====================================================================================%
        \item It is sufficient to find a bijection $g : [0,1) \rightarrow \R$, as it allows us to construct $h : \R \rightarrow \R^2$, as follows:
        \[
        h(x) = (g \times g) \circ f^{-1} \circ g^{-1} (x)
        \]
        which is bijective as it is the composition of bijective functions.

        Finding a bijection $g$ is trivial as we can apply Bernstein’s Theorem on $g_0: [0,1) \rightarrow \R$ with $g_0 (x) = x$ and $g_1 : \R \rightarrow [0,1)$ with $g_1(x) = \frac1\pi \tan^{-1} x + \frac 12$. Proving that these are one to one are trivial.

        \item Lastly, we can use induction to map $\R$ to $\R^n$. Suppose we have a function mapping $\R$ to $\R^{n-1}$. It is sufficient to construct a function mapping $\R^{n-1}$ to $\R^n$. 

        Using $h$ from the previous part, we can construct $h*$, 
        \[
        h(x) = (h_1(x), h_2(x)) \quad \text{then} \quad h^*(x_1, x_2, \dots, x_{n-1}) = (h_1(x_1), h_2(x_1), x_2, \dots, x_{n-1})
        \]
        This is a bijection as it is the composition of bijective functions, thus $\R \asymp \R^n$
    }

}

\bx{ % 0.6.8
    Show that the power set $\mathcal P(\N)$ has the same cardinality as $\R$.
    \sol{
        Construct the following set 
        \[
        A = \{ (a_1, a_2, a_3, \dots) : a_n \in \{0,1\} \}
        \] 
        We will now show that $\mathcal P(\N) \asymp A$. We define the map $f : \mathcal P(\N) \rightarrow A$ as follows 
        \[
        f(X) = (a_1, a_2, a_3, \dots) \quad \text{where} \quad a_n = \begin{cases} 1 & n \in X \\ 0 & n \notin X \end{cases}  
        \]
        \textbf{Injective:} Suppose we have $f(X) = (a_1, a_2, a_3, \dots)$ and $g(Y) = (b_1, b_2, b_3, \dots)$, with $X \ne Y$. Then there exists $n \in \N$, such that $n \in X$ but $n \notin Y$, then $a_n = 1 \ne b_n = 0$. Thus $f$ is one to one.
        \textbf{Surjective:} Given any sequence $(a_1, a_2, a_3, \dots) \in A$, we define $X = \{ n \in \N : a_n = 1 \}$, then $f(X) = (a_1, a_2, a_3, \dots)$.

        Hence, we have shown that $f$ is bijective and $\mathcal P(\N) \asymp A$.

        Next,we will show that $A \asymp \R$ using Bernstein's Theorem in Exercise 0.6.5. We can construct a map $g_0 : A \rightarrow [0,1]$ as follows 
        \[
        g_0(a_1, a_2, a_3, \dots) = \sum_{n=1}^\infty \frac{2a_n}{3^n}
        \]
        \textbf{Injective:} Suppose $(a_1, a_2, \dots) \ne (b_1, b_2, \dots)$. Let $k$ be the first index where they differ, i.e. $a_k \ne b_k$ but $a_i = b_i$ for all $i < n$. Without loss of generality, $a_k = 0$ and $b_k = 1$. Then 
        \[
        g_0(b_1, b_2, \dots) - g_0(a_1, a_2, \dots) 
        =
        \frac{2}{3^k} + \sum_{n > k} \frac{2(b_n - a_n)}{3^n}
        \]
        Since $|b_n - a_n| \le 1$, the tail satisfies 
        \[
        \left| \sum_{n > k} \frac{2(b_n - a_n)}{3^k} \right| \le \sum_{n > k} \frac{2}{3^n} = \frac{1}{3^k}
        \]
        Hence, we get
        \[
        g_0(b_1, b_2, \dots) - g_0(a_1, a_2, \dots) \ge \frac{2}{3^k} - \frac{1}{3^k} > 0
        \]
        Thus showing that $g_0$ is injective

        We will now construct $g_1 : [0,1] \rightarrow A$ as follows
        \[
        g_1 (x) = (a_1, a_2, a_3, \dots) 
        \quad \text{such that} \quad 
        X = \sum_{n=1}^\infty \frac{a_n}{2^n} 
        \]
        For this map, $(a_n) \in A$ will be expressed in the form of recurring $0$’s, i.e. there does not exist $n \in \N$ such that $a_i = 1$ for all $ i > n $. Suppose $x, y \in [0,1]$ such that $x \ne y$. Since sequences of recurring $1$’s are excluded, we get 
        \[
        g_1(x) = (a_1, a_2, a_3, \dots) = (b_1, b_2, b_3, \dots) = g_1(y), \quad \text{where} \quad a_n = b_n \ \forall n \in \N
        \]
        By Bernstein’s Theorem, we can construct $g : A \rightarrow [0,1]$ that is bijective, showing that $A \asymp [0,1]$.

%====================================================================================%

        Lastly, we can map $h : [0,1] \rightarrow \R$ that is bijective, by using Bernstein’s Theorem. We have $h_0 : [0,1] \rightarrow \R$ with $h_0(x) = x$ and $h_1 : \R \rightarrow [0,1]$ with $h_1(x) = \frac1\pi \tan^{-1} x + \frac12$. Proving that $h_0$ and $h_1$ is injective and hence $h$ is bijective is trivial and hence left as an exercise for the reader. Thus, $[0,1] \asymp \R$.

        Combining $f$, $g$ and $h$, we get $\mathcal P(\N) \asymp A \asymp [0,1] \asymp \R$.


    }
}

\bx{ % 0.6.9
    Is it possible to list (all) the rationals in $[0,1]$, written as decimals, so that the entries on the diagonal also give a rational number?
    \sol{
        This is possible. Consider the enumeration of $r_n$ with the condition of $r_n$ having its $n$-th digit being zero. All $r_n$ will be in the form of trailing $0$’s instead of trailing $9$’s. I.e. $0.14$ will be expressed as $0.1400\dots$ instead of $0.1399\dots$ and would have a total of 2 digits.

        Following this construction, $r_1 = 0.\overline{a_1a_2a_3 \dots}$ since it has the digit zero on the first digit. $r_2 = \overline{b_0 0 b_2 b_3 \dots}$ since it has the digit zero on the second digit. Repeating this process, the number along the diagonal would be $0.0000$ which is a rational number.
    }
}